### 2018-09-14 ICRA19/covControl.tex
reviewed the intro and related work, added info on experiments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Shape  Control using Rigid Boundaries}
\label{sec:covControl}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=\linewidth]{SquareFill.pdf} 
\vspace{-1em}
\caption{Pushing the swarm against a square boundary wall allows limited control of the shape of the swarm, as a function of swarm area $A$ and the commanded movement direction $\beta$. Left plot shows locus of possible mean positions for five values of $A$.  %The locus morphs from a square to a circle as $A$ increases.  The covariance ellipse for each $A$ is shown with a dashed line.
 Center shows two corresponding arrangements of kilobots.  At right is $\bar{x}(A), \sigma_{xy}(A), \sigma_x^2(A),$ and $\rho_{xy}(A)$ for a range of $\beta$ values. See online interactive demonstration at \cite{Haoran2016SwarminSquare}.
 }
\label{fig:SquareFill}
\end{center}
\end{figure*} 
\begin{figure*}[!htb]
\begin{center}
\vspace{-1em}
\includegraphics[width=\linewidth]{CircleFill.pdf} 
\vspace{-1em}
\caption{Pushing the swarm against a circular boundary wall allows limited control of the shape of the swarm, as a function of the fill level $h$ and the commanded movement direction $\beta$. Left plot shows locus of possible mean positions for four values of $h$. The locus of possible mean positions are concentric circles. 
At right is $\sigma_{xy}(h), \sigma_x^2(h),$ and $\rho_{xy}(h)$ for a range of $\beta$ values.
See online interactive demonstration at \cite{Haoran2016SwarminCircle}.
}  
\label{fig:CircleFill}
\end{center}
\vspace{-1em}
\end{figure*} 
Shape control using angle of repose only considers the particles that pile up on the object, but most of the particles pass by.
 This section instead focuses on shape control of the entire group when all the particles are pushed against rigid boundaries, starting by examining analytically all possible configurations in two canonical configuration spaces, and then examining the effect of boundary layer friction.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\columnwidth]{friction.pdf} 
\vspace{-1em}
\caption{(a,b) Wall friction reduces the force for going forward $F_{\text{\emph{forward}}}$ on a particle near a wall, but not for a free particle. (c) velocity of a fluid reduces to zero at the boundary.
\label{fig:friction}
}\vspace{-1em}
\end{center}
\end{figure}

@@

\subsection{Efficient control of correlation}
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{ControlledCorrelation.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:ControlledCorrelation}
Analytical results comparing maximum correlation $\rho_{xy}$. Lines labeled \textsf{F} use the boundary layer friction model of \eqref{eq:correlationFriction} with four boundary layer thicknesses $h$ and the stable triangular configuration \eqref{eq:GravityCorrelation}.
}\end{figure}

@@

\section{Experiments}\label{sec:Experiments}
This section reviews three demonstrations of efficient shape control of many particles.
\subsection{Hardware experiment: particle angle of repose}
In this section we varied the approach angle to shape a swarm with a characteristic angle of repose.  
We then showed how the angle of repose can be increased by decreasing the magnitude of the force that moves the particles.
%
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{aorPlot.pdf}
\end{center}
\caption{\label{fig:angleOfReposeExp}
Experimental data using iron particles, varying angle of attack, and three tilt angles to vary the force applied by gravity.
}
\end{figure}
%
%\begin{figure}
%\begin{center}
%	\includegraphics[width=\columnwidth]{ironAndSaltCloseup.pdf}
%\end{center}
%\caption{\label{fig:ironAndSaltCloseup}
%Magnified image of salt and iron at angle of repose.
%}
%\end{figure}
%
The particles used are iron filings (?Company name and particle size?), and the motive force is gravity. 
The particles were poured into a frame composed of two sheets of acrylic with ?? mm spacing between. Five 40 mm rods were epoxied between the sheets at angles 
 $\{0^\circ,15^\circ, 30^\circ, 45^\circ, 60^\circ \}$, generating angle of attacks $\beta = \{90^\circ,75^\circ, 60^\circ, 45^\circ, 30^\circ \}$.
 The frame was tested at three tilt angles with respect to horizontal: $\beta = \{90^\circ,60^\circ, 45^\circ \}$, resulting in $\{100,87, 71\}\%$ of the gravitational force.
 For each test the bottom of the frame was removed to allow unsupported particles to escape and the shape of the remaining particles was measured from photographs taken by a tripod-mounted camera inclined at the same tilt angle as the frame.
  The decreasing tilt angles resulting in increasing angle of repose values: $\alpha = \{42^\circ,50^\circ, 63^\circ \}$
These experiments show how the pile of particles can be used to convey two scalar values: the force applied and the attack angle.  We can also apply varying levels of force and torque to the rod according to \eqref{eq:ForceAOR} and \eqref{eq:TorqueAOR}.

\subsection{Hardware experiment: kilobot angle of repose}
We varied the approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. 
 A Kilobot is a three-centimeter diameter,  low-cost robot. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp}, also showing angle of repose of the Kilobots with  the pink rod at three angles of attack: 90$^\circ$, 67.5$^\circ$ and 45$^\circ$. The green lines show the triangle shape the robots pile up into. The cyan star is the center of mass of the rod, and the mean position and variance of the robots are shown with  red stars and red ellipses.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\caption{\label{fig:SetUp}
Steering Kilobots with lights and characteristic shape formed by Kilobot angle of repose for three angle of attacks.
}
\end{figure}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{newExperiment.pdf}
\end{center}
%\vspace{-1em}
\caption{\label{fig:covExperiment}
Hardware demonstration steering $\approx 50$ kilobot robots to desired covariance. The goal covariance is negative in first 100 seconds and is positive in the next 100 seconds. The actual covariance is shown in different trials. Frames above the plot show output from machine vision system and an overlaid covariance ellipse.
%\vspace{-2.5 em}
}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Shape  Control using Rigid Boundaries}
\label{sec:covControl}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=.8\linewidth]{SquareFill.pdf} 
\vspace{-.8em}
\caption{Pushing the swarm against a square boundary wall allows limited control of the shape of the swarm, as a function of swarm area $A$ and the commanded movement direction $\beta$. Left plot shows locus of possible mean positions for five values of $A$.  %The locus morphs from a square to a circle as $A$ increases.  The covariance ellipse for each $A$ is shown with a dashed line.
 Center shows two corresponding arrangements of kilobots.  At right is $\bar{x}(A), \sigma_{xy}(A), \sigma_x^2(A),$ and $\rho_{xy}(A)$ for a range of $\beta$ values. See online interactive demonstration at \cite{Haoran2016SwarminSquare}.
 }
\label{fig:SquareFill}
\end{center}
\end{figure*} 
\begin{figure*}[!htb]
\begin{center}
\vspace{-1em}
\includegraphics[width=.8\linewidth]{CircleFill.pdf} 
\vspace{-1.em}
\caption{Pushing the swarm against a circular boundary wall allows limited control of the shape of the swarm, as a function of the fill level $h$ and the commanded movement direction $\beta$. Left plot shows locus of possible mean positions for four values of $h$. The locus of possible mean positions are concentric circles. 
At right is $\sigma_{xy}(h), \sigma_x^2(h),$ and $\rho_{xy}(h)$ for a range of $\beta$ values.
See online interactive demonstration at \cite{Haoran2016SwarminCircle}.
}  
\label{fig:CircleFill}
\end{center}
\vspace{-1em}
\end{figure*} 
Shape control using angle of repose only considers the particles that pile up on the object, but most of the particles pass by.
 This section instead focuses on shape control of the entire group when all the particles are pushed against rigid boundaries, starting by examining analytically all possible configurations in two canonical configuration spaces, and then examining the effect of boundary layer friction.

@@

\begin{figure}[tb]
\begin{center}
\includegraphics[width=0.8\columnwidth]{friction.pdf} 
\vspace{-1em}
\caption{(a,b) Wall friction reduces the force for going forward $F_{\text{\emph{forward}}}$ on a particle near a wall, but not for a free particle. (c) velocity of a fluid reduces to zero at the boundary.
\label{fig:friction}
}\vspace{-2em}
\end{center}
\end{figure}

@@

\subsection{Efficient control of correlation}
\begin{figure}[htb]
\begin{center}
	\includegraphics[width=\columnwidth]{ControlledCorrelation.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:ControlledCorrelation}
Analytical results comparing maximum correlation $\rho_{xy}$. Lines labeled \textsf{F} use the boundary layer friction model of \eqref{eq:correlationFriction} with four boundary layer thicknesses $h$ and the stable triangular configuration \eqref{eq:GravityCorrelation}.
}\end{figure}

@@

\section{Experiments}\label{sec:Experiments}
This section reviews three demonstrations of efficient shape control of many particles.
\subsection{Hardware experiment: particle angle of repose}
In this section we varied the approach angle to shape a swarm with a characteristic angle of repose.  
We then showed how the angle of repose can be increased by decreasing the magnitude of the force that moves the particles.
%
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{aorPlot.pdf}
\end{center}
\vspace{-1.5em}
\caption{\label{fig:angleOfReposeExp}
Experimental data using iron particles, varying angle of attack, and three tilt angles to vary the force applied by gravity.
}\vspace{-1.em}
\end{figure}
%
%\begin{figure}
%\begin{center}
%	\includegraphics[width=\columnwidth]{ironAndSaltCloseup.pdf}
%\end{center}
%\caption{\label{fig:ironAndSaltCloseup}
%Magnified image of salt and iron at angle of repose.
%}
%\end{figure}
%
The particles used are iron filings (Dowling Magnets, \#731019, $\approx0.5$~mm diameter), and the motive force is gravity. 
The particles were poured into a frame composed of two sheets of acrylic with 4.5 mm spacing between. Five 40 mm rods were epoxied between the sheets at angles 
 $\{0^\circ,15^\circ, 30^\circ, 45^\circ, 60^\circ \}$, generating angle of attacks $\beta = \{90^\circ,75^\circ, 60^\circ, 45^\circ, 30^\circ \}$.
 The frame was tested at three tilt angles with respect to horizontal: $\beta = \{90^\circ,60^\circ, 45^\circ \}$, resulting in $\{100,87, 71\}\%$ of the gravitational force.
 For each test the bottom of the frame was removed to allow unsupported particles to escape and the shape of the remaining particles was measured from photographs taken by a tripod-mounted camera inclined at the same tilt angle as the frame.
  The decreasing tilt angles resulting in increasing angle of repose values: $\alpha = \{42^\circ,50^\circ, 63^\circ \}$
These experiments show how the pile of particles can be used to convey two scalar values: the force applied and the attack angle.  These result in varying levels of force and torque on the rod according to \eqref{eq:ForceAOR} and \eqref{eq:TorqueAOR}.

\subsection{Hardware experiment: kilobot angle of repose}
We varied the approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. 
 A Kilobot is a three-centimeter diameter,  low-cost robot. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp}, also showing angle of repose of the Kilobots with  the pink rod at three angles of attack: 90$^\circ$, 67.5$^\circ$ and 45$^\circ$. The green lines show the triangle shape the robots pile up into. The cyan star is the center of mass of the rod, and the mean position and variance of the robots are shown with  red stars and red ellipses.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1.5em}
\caption{\label{fig:SetUp}
Steering Kilobots with lights and characteristic shape formed by Kilobot angle of repose for three angle of attacks.
}
\end{figure}

@@

\begin{figure}[!htb]
\begin{center}
	\includegraphics[width=\columnwidth]{newExperiment.pdf}
\end{center}
\vspace{-2em}
\caption{\label{fig:covExperiment}
Hardware demonstration steering $\approx 50$ kilobot robots to desired covariance. The goal covariance is negative in first 100 seconds and is positive in the next 100 seconds. The actual covariance is shown in different trials. Frames above the plot show output from machine vision system and an overlaid covariance ellipse.
%\vspace{-2.5 em}
}
\end{figure}

### 2018-09-14 ICRA19/relatedWork.tex
removed patent citation
reviewed the intro and related work, added info on experiments.

Shape, or relative position, control of many particles is necessary for a range of applications. Therefore, it has been a topic of research from a control perspective in both centralized and distributed approaches. 
 This paper focuses on centralized approach that apply the uniform control input to all the particles. To change the relative position of the particles, we need to break the symmetry caused by the uniform input.
Symmetry can be broken using particles that respond differently to the uniform control signal, either through agent-agent reactions \cite{bertozzi2015ring}, or engineered inhomogeneity  \cite{Donald2013,bretl2007,beckerIJRR2014}. 
 The magnetic gradients of MRI scanners are \emph{uniform}, meaning the same force is applied everywhere in the workspace\cite{nosrati2018development}.
%Controlling the \emph{shape}, or relative positions, of many particles is a key ability for a range of applications.  Correspondingly, it has been studied from a control-theoretic perspective in  both centralized and decentralized approaches.
% For examples of each, see the centralized virtual leaders in \cite{egerstedt2001formation}, and the  gradient-based decentralized controllers  using control-Lyapunov functions in~\cite{hsieh2008decentralized}. 
%However, these approaches assume a level of intelligence and autonomy in individual robots that exceeds the capabilities of many systems, including current micro- and nano-robots.  Current micro- and nano-robots, such as those in~\cite{Chowdhury2015,martel2015magnetotactic,Xiaohui2015magnetiteMicroswimmers} lack onboard computation.

%This paper focuses on centralized techniques that apply the same control input to both particles. 
%Precision control requires breaking the symmetry caused by the uniform input.  
%Symmetry can be broken using particles that respond differently to the uniform control signal, either through agent-agent reactions \cite{bertozzi2015ring}, or engineered inhomogeneity  \cite{Donald2013,bretl2007,beckerIJRR2014}. 
% The magnetic gradients of MRI scanners are \emph{uniform}, meaning the same force is applied everywhere in the workspace\cite{nosrati2018development}.
 This work assumes a uniform control with homogenous particles, as in~\cite{AaronManipulation2013}, and breaks the control symmetry using obstacles in the workspace.

%The techniques in this paper are inspired by artificial force-fields.

%\emph{Fluid-flow:} 
%Fluid flow along boundaries generates a shear force that pushes different parts of a body in opposing directions. 
%Most introductory fluid dynamics textbooks provide models~\citep{Munson2013}.
%Similarly, a swarm of robots under global control pushed along a boundary will experience shear forces.  
%This is a position-dependent force, and so can be exploited to control the configuration or shape of the swarm.  
% \citep{spears2006physics}~used these forces to disperse a swarm's spatial position for coverage for physics-based swarm simulations.

%\emph{Artificial Force-fields:}
%Much research has focused on generating non-uniform artificial force-fields that can be used to rearrange passive components.

Alternative techniques rely on non-uniform inputs, such as artificial force-fields. 
Much recent work in magnet control has focused on exploiting inhomogeneities in the magnetic field to control multiple micro particles using gradient-based pulling~\cite{Salmanipour2018EightDOF,Denasi2018independent}.  
Using large-scale external magnetic fields makes it challenging to independently control more than one microrobot unless the distance between the electromagnetic coils is at the same length scales as the robot workspace~\cite{diller2016six, Denasi2018independent, Salmanipour2018EightDOF }.
%Applications have included techniques to design shear forces for sensorless manipulation of a single object by~\cite{lamiraux+2001:ra}.  
%\cite{vose2012sliding} demonstrated a collection of 2D force fields generated by six degree-of-freedom vibration inputs to a rigid plate.  These force fields, including shear forces, could be used as a set of primitives for motion control to steer the formation of multiple objects. %However unlike the uniform control model in this paper, their control was multi-modal and position-dependent.
%\todo{talk about obstacles, think about adding goldberg}

>>>>

Controlling the relative position of many particles is necessary for a range of applications. Therefore, it has been a topic of research from a control perspective in both centralized and decentralized approaches.

 This paper focuses on centralized approaches that apply uniform control inputs to all the particles. To change the relative position of the particles, we need to break the symmetry caused by the uniform input.
Symmetry can be broken using particles that respond differently to the uniform control signal, either through agent-agent reactions \cite{bertozzi2015ring}, or engineered inhomogeneity  \cite{Donald2013,bretl2007,beckerIJRR2014}. 
Some examples of global inputs include magnetic fields and acoustic radiation forces. The magnetic gradients of MRI scanners are \emph{uniform}, meaning the same force is applied everywhere in the workspace \cite{nosrati2018development}. Similarly, a single acoustic vibration source can be exploited for simultaneous positioning many particles~\cite{oberti2007manipulation,zhou2016controlling}.

%Controlling the \emph{shape}, or relative positions, of many particles is a key ability for a range of applications.  Correspondingly, it has been studied from a control-theoretic perspective in  both centralized and decentralized approaches.
% For examples of each, see the centralized virtual leaders in \cite{egerstedt2001formation}, and the  gradient-based decentralized controllers  using control-Lyapunov functions in~\cite{hsieh2008decentralized}. 
%However, these approaches assume a level of intelligence and autonomy in individual robots that exceeds the capabilities of many systems, including current micro- and nano-robots.  Current micro- and nano-robots, such as those in~\cite{Chowdhury2015,martel2015magnetotactic,Xiaohui2015magnetiteMicroswimmers} lack onboard computation.
%This paper focuses on centralized techniques that apply the same control input to both particles. 
%Precision control requires breaking the symmetry caused by the uniform input.  
%Symmetry can be broken using particles that respond differently to the uniform control signal, either through agent-agent reactions \cite{bertozzi2015ring}, or engineered inhomogeneity  \cite{Donald2013,bretl2007,beckerIJRR2014}. 
% The magnetic gradients of MRI scanners are \emph{uniform}, meaning the same force is applied everywhere in the workspace\cite{nosrati2018development}.
 This work assumes a uniform control with homogenous particles, as in~\cite{AaronManipulation2013}, and breaks the control symmetry using obstacles in the workspace. 
  While in \cite{shahrokhi2018TRO} we showed how to control the mean position and variance through repeated collisions with the workspace, this paper focuses on stable configurations using few pushes. 
   In \cite{AaronManipulation2013} we showed that single obstacle can be used to rearrange $n$ particles using an $O(n^2)$-time algorithm.
   In~\cite{shahrokhi2017}, we gave algorithms that could adjust the position of $n$ particles in an environment with walls that have non-slip contacts in $O(n^2)$-time. %We assumed that if a particle is pushed into a wall, it will not move until a uniform input pulls it from the wall.

%The techniques in this paper are inspired by artificial force-fields. 
%\emph{Fluid-flow:} 
%Fluid flow along boundaries generates a shear force that pushes different parts of a body in opposing directions. 
%Most introductory fluid dynamics textbooks provide models~\citep{Munson2013}.
%Similarly, a swarm of robots under global control pushed along a boundary will experience shear forces.  
%This is a position-dependent force, and so can be exploited to control the configuration or shape of the swarm.  
% \citep{spears2006physics}~used these forces to disperse a swarm's spatial position for coverage for physics-based swarm simulations.
%\emph{Artificial Force-fields:}
%Much research has focused on generating non-uniform artificial force-fields that can be used to rearrange passive components.

Alternative techniques often rely on non-uniform inputs.
 Much recent work in magnet control has focused on exploiting inhomogeneities in the magnetic field to control multiple micro particles using gradient-based pulling~\cite{Salmanipour2018EightDOF,Denasi2018independent}.  
Using large-scale external magnetic fields makes it challenging to independently control more than one microrobot unless the distance between the electromagnetic coils is at the same length scales as the robot workspace~\cite{diller2016six}.

 Many other shape control techniques rely on agent intelligence.
 These include distributed approaches where each agent has a map of the desired shape and its position~\cite{bandyopadhyay2017probabilistic,rubenstein2014programmable}; %bandyopadhyay2017probabilistic to shape control a large number of agents has probabilistic swarm guidance using inhomogeneous Markov chains
  agents that do not communicate, but sense local environmental cues to determine where to spend more time~\cite{li2017decentralized};
 % Another work considers agents are not communicating and give probabilistic results by only measuring a scalar distance between the agents \cite{li2017decentralized}. 
 or workspace designs that direct or trap agents as in~\cite{fine2013eliciting}.
 % Same agents in a group that might behave differently due to their place in the environment inspired by birds or ants \cite{fine2013eliciting}. 
 %As in \cite{li2017decentralized,fine2013eliciting}, this paper uses the workspace to shape the particles.
%Because this paper assumes the particles can neither communicate nor compute, a centralized controller is necessary.
%However, using autonomous approaches for positioning a large group of particles is not practical in our approach because the particles do not have that level of intelligence. 
%Applications have included techniques to design shear forces for sensorless manipulation of a single object by~\cite{lamiraux+2001:ra}.  
%\cite{vose2012sliding} demonstrated a collection of 2D force fields generated by six degree-of-freedom vibration inputs to a rigid plate.  These force fields, including shear forces, could be used as a set of primitives for motion control to steer the formation of multiple objects. %However unlike the uniform control model in this paper, their control was multi-modal and position-dependent.
%\todo{talk about obstacles, think about adding goldberg}
